\section{Limitations}

We are candid about the boundaries of what these results establish. Every detection metric reported here comes from offline replay of recorded \texttt{/lowstate} CSV logs, not from live on-robot inference; we have verified numerical equivalence between the research and deployment paths (max $|\Delta| \le 3.8\times10^{-7}$ on the detection output over the test windows), but that only shows the shipped runtime reproduces the offline model, not that the same detection accuracy holds during closed-loop operation on hardware. The latency numbers share this caveat. The reported mean of $\approx 1.0$ ms/window and p95 of $\approx 1.3$ ms are measured on a single CPU thread of a development machine running the ONNX deployment runtime, comfortably inside the 2.0 ms budget at 500 Hz, but they are not a benchmark on the Go2's onboard computer, where scheduling, thermal, and contention conditions differ.

The evidence is also thin in places that matter. The positive set is small: 15 entanglement events across 25 recordings, and the front-right leg appears in only 3 recordings. This under-representation is the most likely driver of the high variance we observe in leave-one-recording-out cross-validation (F1 $= 0.807 \pm 0.142$) and of the weaker per-leg front-right precision (0.467) reported in Table~\ref{tab:perleg}. Severity is another soft spot. No ground-truth severity labels exist, so the physics index $I_{\text{leg}} = g\cdot\sqrt{d\cdot r}$ is reported as a calibrated index rather than a measured force, and it is validated only qualitatively; the network intensity head that we blend with it is a weak auxiliary trained against a physics pseudo-target, not against independent measurements. On calibration, temperature scaling ($T = 5.918$) de-saturates the raw probabilities and slightly improves the Brier score (0.128 to 0.118) but does \emph{not} improve reliability: ECE actually worsens (0.134 to 0.156). Finally, our only comparison baseline under this protocol is the rule-based thigh-torque heuristic; learned or statistical detectors (for example a gradient-boosted-tree baseline) were not evaluated under the same leakage-safe, grouped split, so we cannot yet position the model against that broader class of methods.