\subsection{Runtime Architecture}
\label{sec:runtime}

On the robot the detector is a ROS~2 node that turns the raw telemetry stream into a published
state estimate. The same preprocessing and model serve offline training and online inference, and only the exported ONNX model together with the saved normalization and calibration statistics cross the deploy boundary.

The node subscribes to \texttt{/lowstate} with \texttt{BEST\_EFFORT} quality of service. Reliable
delivery would add retransmission latency to a stream that arrives hundreds of times per second, and
a dropped proprioceptive sample matters far less than a late one, so trading guaranteed delivery for
low latency is the right call. Each message is adapted into the 48 raw signals the model expects and
pushed into a 200-sample circular ring buffer; the buffer holds memory and per-sample cost constant,
since the oldest sample is overwritten as each new one arrives rather than reallocating a growing
window. Once the buffer is full it is expanded to the 60-channel representation and normalized with
the statistics saved at training time.

Inference runs through ONNX Runtime rather than PyTorch. The exported graph loads faster, uses less
memory, and removes the training-framework dependency from the robot, which matters on a constrained
onboard target~\cite{onnxruntime,macenski2022ros2}. The detection logit is passed through a sigmoid
and, separately, through a temperature-scaled sigmoid ($T=5.918$) to produce the reported confidence;
the per-leg severity is the equal-weight blend of the network head and the physics index. Raw network
predictions flicker from sample to sample, so a detection is latched only after the raw probability
stays above threshold for 75~ms. That short temporal debounce suppresses isolated spikes without
noticeably delaying a genuine alarm. Per-leg thresholds then name the affected leg, with the
rear-right threshold raised to 0.9 because that leg was the most prone to false positives; the others
use 0.5. The node publishes
\texttt{/entanglement\_state}, carrying the debounced flag, the calibrated confidence, four per-leg
probabilities, four per-leg severities, and the name of the alarm leg.

\subsubsection{Stationarity gate}
One failure mode surfaced only in testing. When the robot walks, stops, and then stiffens into the
rigid Lock stance it holds after standing up, the ring buffer still contains the tail of the walking
motion, and the detector can briefly report entanglement for a robot that is simply standing still.
The gate that fixes this watches the mean absolute joint velocity: when it falls below 0.30~rad/s for
100~ms the robot is treated as stationary, and the node clears the ring buffer, resets the debounce
counter, and arms a 300~ms suppression window that ignores the transient while gait is re-acquired.
The gate is edge-triggered, so it acts once on the transition rather than continuously. It is disabled
in the research configuration so that the evaluation pipeline is byte-identical to the deployed one,
and enabled only on the robot.
